### 2019-08-08 thesis.tex
* thesis.tex: Summary: new text

\section{Solar and space physics}
\label{sec:solar-physics}
The domain of solar and space physics is the \emph{heliosphere}, a cavity in
the interstellar medium, created by the constant supersonic flow of solar
plasma that permeates the interplanetary space. This region encloses the solar
system and extends for approximately $140\unit{AU}$ in the surrounding galactic
space. Its outer limit is the \emph{heliopause}, an interface zone where the
outgoing pressure of the solar plasma balances the incoming pressure from the
interstellar medium. This comet-shaped plasma bubble, has an inner boundary, the
\emph{termination shock}, which delimits the sphere of absolute influence of the
solar plasma. Outside the termination shock, the solar wind particles start to
be subjected to increasing external pressure, transitioning to a subsonic flow
that blends with the interstellar medium at roughly $100\unit{AU}$ from the Sun.
Beyond the termination shock, lies the heliosheath, a so-far-unexplored zone
that extends out to the heliopause, separating the solar domain from the nearby
galactic region \cite{NAP13060}. In \autoref{figD1}, we have a depiction of the
regions and boundaries described above, and the current location of both Voyager
missions, that are already outside the heliosphere, in the interstellar space.
\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.9\textwidth]{solar_system_env.png}
    \caption{Main boundaries of the heliosphere and the location of both
      Voyager missions.}
      {\footnotesize Credit:}
      \href{https://voyager.jpl.nasa.gov/news/details.php?article_id=112}
      {\footnotesize NASA/JPL-Caltech}{\footnotesize , accessed at 08/08/2019.}
    \label{figD1}
  \end{center}
\end{figure}

Solar physics can be thought of as a combination of plasma and space physics.

>>>>

\section{Solar and space physics}
\label{sec:solar-physics}
The domain of solar and space physics is the \emph{heliosphere}, a cavity in
the interstellar medium, created by the constant supersonic flow of solar
plasma that permeates the interplanetary space. This region encloses the solar
system and extends for approximately $140\unit{AU}$ in the surrounding galactic
space. Its outer limit is the \emph{heliopause}, an interface zone where the
outgoing pressure of the solar plasma balances the incoming pressure from the
interstellar medium. This comet-shaped plasma bubble \cite{Dialynas2017}, has
an inner boundary, the \emph{termination shock}, which delimits the sphere
of absolute influence of the solar plasma. Beyond the termination shock, at
roughly $100\unit{AU}$ from the Sun, extending out to the heliopause, is the
heliosheath. In this region, the solar wind particles start being subjected to
increasing external pressure, transitioning to a subsonic, turbulent flow that
blends and interacts directly with the matter in the local interstellar medium
\cite{NAP13060}. In \autoref{figD1}, we have a depiction of the regions and
boundaries described above, and the current location of both Voyager missions,
that are already outside the heliosphere, in the interstellar space.
\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.9\textwidth]{solar_system_env.png}
    \caption{Main boundaries of the heliosphere and the location of both
      Voyager missions.}
      {\footnotesize Credit:}
      \href{https://voyager.jpl.nasa.gov/news/details.php?article_id=112}
      {\footnotesize NASA/JPL-Caltech}{\footnotesize , accessed at 08/08/2019.}
    \label{figD1}
  \end{center}
\end{figure}

Inside the heliosphere, the solar and space physics research aims to understand
the history, evolution and dynamics of the Sun and its effects on Earth's space
environment. Besides that, the interplanetary system provide an accessible

subjected to direct and relatively close action of
the solar wind and radiation, lies our planet, Earth.

The energy the Sun
dumps over the Earth, in the form of visible light, ultraviolet and X-ray
radiation, not only determines the temperature, shape of the terrestrial
upper atmosphere and ionosphere, but also is responsible for the life as
we know it.
